Analysis and results

### 2021-12-08 analysis/03_analysis.Rmd
Cleaned up analysis markdown

```{r model-calibration, eval=FALSE}
intercept <- 0                            # Intercept-only
interactions <- 0                         # Include interactions with the intercept-only model?
public_affairs <- 1                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

# # ##############################
# X_new <- array(NA, dim = c(dim(X)[1:3], 21)) # 13 + interactions
# for (r in 1:dim(X)[1]) {
#   for (s in 1:dim(X)[2]) {
#     X_new[r,s,,] <- X[r,s,,c(1:13, 56:63)] # 13 + interactions
#   }
# }
# X <- X_new
# # ##############################

@@

# ####################################################################################
# # if (intercept == 0) {
#   # OLD...
#   # Replace factor labels with levels
#   Z_old <- Z %>%
#   # Z <- Z %>%
#     mutate_if(is.factor, as.integer) %>%
#     mutate_if(is.integer, as.factor)
#   
#   # Pad the variables names with _
#   # colnames(Z) <- str_c(colnames(Z), "_")
#   colnames(Z_old) <- str_c(colnames(Z_old), "_")
#   
#   # Use the output of lm to get a dummy-coded version of the covariate matrix Z
#   # Z$y <- matrix(rnorm(nrow(Z)), ncol = 1)
#   # out <- lm(y ~ ., Z, x = TRUE)
#   Z_old$y <- matrix(rnorm(nrow(Z_old)), ncol = 1)
#   out <- lm(y ~ ., Z_old, x = TRUE)
#   
#   # Save out Z as a matrix, including an intercept
#   Z_old <- tibble(intercept = rep(1, dim(X)[1])) %>%
#   # Z <- tibble(intercept = rep(1, dim(X)[1])) %>%
#     bind_cols(as_tibble(out$x[,-1])) %>%
#     as.matrix()
#   
#   # NEW...
#   # Replace factor labels with levels and NAs with 0s
#   Z_new <- Z %>%
#     mutate_if(is.factor, as.integer) %>%
#     mutate_if(is.integer, as.factor) %>% 
#     replace(is.na(.), 0) %>% 
#     # Use dummy_cols() to get a dummy-coded version of factors
#     dummy_cols(
#       remove_first_dummy = TRUE,
#       remove_selected_columns = TRUE
#     ) %>% 
#     # Include an intercept, sort columns numerically, save as matrix
#     bind_cols(tibble(intercept = rep(1, dim(X)[1]))) %>% 
#     relocate(intercept, sort(colnames(.))) %>% 
#     as.matrix()
# # }
# 
# 
# 
# 
# ####################################################################################

@@

```{r extract-draws, eval=FALSE}
intercept <- 1                            # Intercept-only
interactions <- 1                         # Include interactions with the intercept-only model?
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

>>>>

```{r model-calibration, eval=FALSE}
intercept <- 0                            # Intercept-only
interactions <- 0                         # Include interactions with the intercept-only model
public_affairs <- 1                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

@@

@@

if (intercept == 0) {
  # Replace factor labels with levels
  Z <- Z %>%
    mutate_if(is.factor, as.integer) %>%
    mutate_if(is.integer, as.factor)

  # Save out Z as a matrix, including an intercept
  Z <- tibble(intercept = rep(1, dim(X)[1])) %>%
    bind_cols(as_tibble(out$x[,-1])) %>%
    as.matrix()
}

@@

```{r extract-draws, eval=FALSE}
intercept <- 1                            # Intercept-only
interactions <- 1                         # Include interactions with the intercept-only model
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics
